---
title             : "Lab 8 Updated"
shorttitle        : "Practicing creating APA manuscript"

author: 
  - name          : "Joanna"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "joanna@email.com"
  - name          : "Thuy"
    affiliation   : "2"
    corresponding : no    # Define only one corresponding author
    address       : "Postal address"
    email         : "thuy@email.com"
  - name          : "Asha"
    affiliation   : "3"
    corresponding : no    # Define only one corresponding author
    address       : "Postal address"
    email         : "asha@email.com"

affiliation:
  - id            : "1"
    institution   : "University of Oregon"
  - id            : "2"
    institution   : "University of R"
  - id            : "3"
    institution   : "University of Data Science"

authornote: |
  We are also affilicated with EDLD 610 Introduction to Data Science.

abstract: |
  Example of abstract goes here. 
  <!-- https://tinyurl.com/ybremelq -->

  
keywords          : "learning, R, takes, practice"
wordcount         : no

bibliography      : ["lab_8_updated_bibliography.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE, echo = FALSE, fig.width = 6.5, fig.height = 8}
#install.packages("kableExtra")
library("papaja")
library("tidyverse")
library("dplyr")
library("rio")
library("here")
library("janitor")
library("knitr")
library("kableExtra")
library("ggplot2")
library("here")
library("devtools")
```

```{r}
here("star.csv")
star <- import(here("data", "star.csv"))
```


```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)

```


```{r}

star <- star %>%
  group_by(sex, frl) %>% 
  mutate(math_mean = round(mean(tmathss),2),
         math_sd = round(sd(tmathss),2),
         rdg_mean = round(mean(treadss),2),
         rdg_sd = round(sd(treadss),2))

star <- star %>% 
  select("sex", "frl", "math_mean", "math_sd", "rdg_mean", "rdg_sd")

# I tried kable but it doesn't seem to work. 
kable(digits = 2,
        col.names = c("sex", "frl", "math_mean", "math_sd", "rdg_mean", "rdg_sd"),
        format = "html") %>% 
  kable_styling(bootstrap_options = c("striped", "condensed"))


# How can we make 4 rows, 2 for boys and 2 for girls, and each has 1 yes and 1 no for frl?



```

In average, girls score higher in both math and reading subjects. 


# Introduction 
 
Many researchers have used the World Survey Data to investigate happiness [@easterlin2009happiness]. For example, @snoep2008religiousness found an association between happiness and religiosity...etc etc... 

# Methods

## Participants

## Material

## Procedure

## Data analysis

# Results

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "lab_8_updated_bibliography.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
```{r plot}
#Create a plot
ggplot(star, aes(x = totexp , y = tmathss)) +
  geom_point() + geom_smooth() + xlab("Teacher Experience (years)") + ylab("Total Math Scale Score") + theme(legend.position = "bottom")
```

```{r, table}
library(kableExtra)
star %>%
  kable()%>%
  kable_styling(bootstrap_options = "striped", full_width = F)
  
  
```


