---
title             : "Lab 8 Updated"
shorttitle        : "Practicing creating APA manuscript"

author: 
  - name          : "Joanna"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "joanna@email.com"
  - name          : "Thuy"
    affiliation   : "2"
    corresponding : no    # Define only one corresponding author
    address       : "Postal address"
    email         : "thuy@email.com"
  - name          : "Asha"
    affiliation   : "3"
    corresponding : no    # Define only one corresponding author
    address       : "Postal address"
    email         : "asha@email.com"

affiliation:
  - id            : "1"
    institution   : "University of Oregon"
  - id            : "2"
    institution   : "University of R"
  - id            : "3"
    institution   : "University of Data Science"

authornote: |
  We are also affilicated with EDLD 610 Introduction to Data Science.

abstract: |
  Example of abstract goes here. 
  <!-- https://tinyurl.com/ybremelq -->

  
keywords          : "learning, R, takes, practice"
wordcount         : no

bibliography      : ["lab_8_updated_bibliography.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE, echo = FALSE, fig.width = 6.5, fig.height = 8}
library("papaja")
library("tidyverse")
library("dplyr")
library("rio")
library("here")
library("janitor")
```

```{r}
here("star.csv")
star <- import(here("data", "star.csv"))
```


```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Introduction 
 
Many researchers have used the World Survey Data to investigate happiness [@easterlin2009happiness]. For example, @snoep2008religiousness found an association between happiness and religiosity...etc etc... 

# Methods

## Participants

## Material

## Procedure

## Data analysis

# Results

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "lab_8_updated_bibliography.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
